\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}

\title{College Algebra Worksheet 3.5}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\begin{center}
    \textit{note: No graphing calculators or electronic devices may be used on this worksheet.}    
\end{center}

\section*{Problem Set 1\\Difficulty level: Normal}
\subsection*{Problem 1}
The graph of \(y=f(-x-2)+3\) is the graph of \(y=f(x)\)
\begin{enumerate}[label=(\alph*)]
    \item reflected over the \( x \)-axis and shifted right 2 units and up 3 units
    \item reflected over the \( y \)-axis and shifted right 2 units and up 3 units
    \item reflected over the \( x \)-axis and shifted left 2 units and up 3 units
    \item reflected over the \( y \)-axis and shifted left 2 units and up 3 units
\end{enumerate}

\subsection*{Problem 2}
Is the function shown in the following graph even, odd, or neither?
    \begin{center}
    \begin{tikzpicture}
    \begin{axis}[
        axis lines=middle,
        width=10cm,
        height=8cm,
        xmin=-6, xmax=6,
        ymin=-6, ymax=6,
    ]
    \addplot[red, thick, domain=-2:6, samples=100] {-x^3+2};
    \end{axis}
    \end{tikzpicture}
    \end{center}

\subsection*{Problem 3}
Is the function shown in the following graph even, odd, or neither?
    \begin{center}
    \begin{tikzpicture}
    \begin{axis}[
        axis lines=middle,
        width=10cm,
        height=8cm,
        xmin=-6, xmax=6,
        ymin=-6, ymax=6,
    ]
    \addplot[red, thick, domain=-2:6, samples=100] {x^3};
    \end{axis}
    \end{tikzpicture}
    \end{center}

\subsection*{Problem 4}
Is the function shown in the following graph even, odd, or neither?
    \begin{center}
    \begin{tikzpicture}
    \begin{axis}[
        axis lines=middle,
        width=10cm,
        height=8cm,
        xmin=-6, xmax=6,
        ymin=-6, ymax=6,
    ]
    \addplot[red, thick, domain=-6:6, samples=100] {x+2};
    \end{axis}
    \end{tikzpicture}
    \end{center}

\newpage
\subsection*{Problem 5}
Is the function shown in the following graph even, odd, or neither?
    \begin{center}
    \begin{tikzpicture}
    \begin{axis}[
        axis lines=middle,
        width=10cm,
        height=8cm,
        xmin=-6, xmax=6,
        ymin=-6, ymax=6,
    ]
    \addplot[red, thick, domain=-6:6, samples=100] {(x-2)^2+1};
    \end{axis}
    \end{tikzpicture}
    \end{center}
    
\subsection*{Problem 6}
Determine if the function is even, odd, or neither.
\[h(x)=6x^5-5x^3+2x\]

\subsection*{Problem 7}
For the following exercises, write a formula for the function obtained when the graph is shifted as described.
\begin{enumerate}
    \item[(a)] \( f(x) = \sqrt{x} \) is shifted up 1 unit and to the left 2 units.
    
    \item[(b)] \( f(x) = |x| \) is shifted down 3 units and to the right 1 unit.
    
    \item[(c)] \( f(x) = \dfrac{1}{x} \) is shifted down 4 units and to the right 3 units.
    
    \item[(d)] \( f(x) = \dfrac{1}{x^2} \) is shifted up 2 units and to the left 4 units.
\end{enumerate}

\subsection*{Problem 8}
How can you determine whether a function is odd or even from the formula of the function?

\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
\begin{enumerate}
    \item[(d)] reflected over the \( y \)-axis and shifted left 2 units and up 3 units.
\end{enumerate}


\subsection*{Problem 2}
neither, since fails both symmetry tests.

\subsection*{Problem 3}
odd, since it is symmetric about the origin.

\subsection*{Problem 4}
neither, since fails both symmetry tests.

\subsection*{Problem 5}
neither, since fails both symmetry tests.

\subsection*{Problem 6}
odd, since \( h(-x) = -h(x) \).

\subsection*{Problem 7}
\begin{enumerate}
    \item[(a)] \( \boxed{f(x) = \sqrt{x + 2} + 1} \)
    \item[(b)] \( \boxed{f(x) = |x - 1| - 3} \)
    \item[(c)] \( \boxed{f(x) = \dfrac{1}{x - 3} - 4} \)
    \item[(d)] \( \boxed{f(x) = \dfrac{1}{(x + 4)^2} + 2} \)
\end{enumerate}

\subsection*{Problem 8}
\begin{itemize}
    \item Even: Check if \( f(-x) = f(x) \)
    \item Odd: Check if \( f(-x) = -f(x) \)
    \item neither, if otherwise.
\end{itemize}

\end{document}
