\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 6}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}

\section*{Problem 1}
A master chef mixes potatoes, onions, and lettuce to obtain a 25 oz package worth 20 dollars. If potatoes, onions, and lettuce cost 14, 31, and 62 cents per oz respectively, and the amount of onions is equal to the amount of lettuce, \textbf{write a system of equations} that can be used to find how much of each is in the package.

\section*{Problem 2}
Compute:
\begin{enumerate}[label=(\alph*)]
    \item \( 125^{\frac{2}{3}} = \)
    \item \( 9^3 9^2 = \)
    \item \( 7^{-4} 7^2 = \)
    \item \( \frac{11^9}{11^7} = \)
    \item \( \left(8^3\right)^4 = \)
    \item \( \left(\frac{7}{4}\right)^2 = \)
\end{enumerate}

\section*{Problem 3}
Let \( f(x) = 8^{x-2} \) and \( g(x) = 4^{2x} \), find the following values:
\begin{enumerate}[label=(\alph*)]
    \item \( f(2) = \)
    \item \( g(2) = \)
\end{enumerate}

\section*{Problem 4}
Because of an economic downturn, the population of a certain urban area declines at the rate of 1.5\% per year. Initially, the population is 350{,}000. To the nearest person, what is the population after three years?

\section*{Problem 5}
A nutritionist is creating a 40 oz blend of grains using oats, barley, and rye. Oats cost 20 cents per oz, barley 30 cents per oz, and rye 50 cents per oz. The total cost of the mixture is \$14. If the amount of barley used is twice the amount of rye, \textbf{write a system of equations} that can be used to find the amount of each grain in the blend.

\section*{Problem 6}
Compute:
\begin{enumerate}[label=(\alph*)]
    \item \( \left(3^4\right)^2 = \)
    \item \( \left(\frac{5}{2}\right)^3 = \)
    \item \( 16^{\frac{3}{4}} = \)
    \item \( \frac{10^6}{10^4} = \)
    \item \( 6^0 = \)
    \item \( 2^{-5} = \)
\end{enumerate}

\section*{Problem 7}
Let \( f(x) = 2^{x+1} \) and \( g(x) = 16^{x-1} \). Evaluate the following:
\begin{enumerate}[label=(\alph*)]
    \item \( f(0) = \)
    \item \( g(2) = \)
\end{enumerate}

\section*{Problem 8}
A piece of equipment depreciates at a constant rate of 4.2\% per year. If its initial value is \$15{,}000, what will be its value after 5 years? Round your answer to the nearest cent.

\section*{Problem Set 2\\Difficulty level: Hard}
\section*{Problem 1}
A city's population was 800,000 in the year 2000. Over the next several years, the population decreased by 2.5\% annually due to migration and economic factors. However, starting in 2010, new policies slowed the decline to 1\% annually. Assuming exponential decay, what is the estimated population in the year 2020?

(Hint: Apply exponential decay in two phases: from 2000 to 2010, then from 2010 to 2020.)


\end{document}
