\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 7}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\section*{Problem 1}
Graph the following functions:
\begin{enumerate}[label=(\alph*)]
    \item \( f(x) = 3^x \)
    \item \( g(x) = 3^{x - 2} \)
    \item \( t(x) = 3^x + 2 \)
\end{enumerate}

\section*{Problem 2}
Solve each equation:
\begin{enumerate}[label=(\alph*)]
    \item \( 9^x = 3 \)
    \item \( -3^x = -27 \)
    \item \( 10^{2x} = 1000 \)
\end{enumerate}

\section*{Problem 3}
Suppose \$1000 is invested for 10 years at 6\% compounded annually.\\
Find the compound amount using the formula:
\[
S = P\left(1 + \frac{r}{n} \right)^{nt}
\]

\section*{Problem 4}
The population of a town of 10,000 grows at the rate of 4\% per year.\\
Find the population five years from now.

\section*{Problem 5}
The number of grams of a certain radioactive substance present at time \( t \) is given by the formula:
\[
A(t) = 300e^{-0.007t}
\]
where \( t \) is the number of years.

\begin{itemize}
    \item How many grams are present at time \( t = 0 \)?
    \item How many grams are present at time \( t = 175 \)? (Round to the nearest gram)
\end{itemize}

\section*{Problem 6}
Graph the following functions:
\begin{enumerate}[label=(\alph*)]
    \item \( h(x) = 2^{-x} \)
    \item \( k(x) = 5^{x+1} \)
\end{enumerate}

\section*{Problem 7}
The value of a car purchased for \$30{,}000 decreases according to the formula:
\[
V(t) = 30000e^{-0.15t}
\]
where \( t \) is the number of years since purchase.

\begin{itemize}
    \item What is the value of the car after 5 years? (Round to the nearest dollar)
    \item After how many full years will the car be worth less than \$10{,}000?
\end{itemize}

\section*{Problem Set 2\\Difficulty level: Hard}
\section*{Problem 1}
A scientist is studying the growth of a bacteria culture. The number of bacteria present at time \( t \) (in hours) is modeled by the equation:
\[
N(t) = 250 \cdot 2^{0.3t}
\]

\begin{itemize}
    \item[(a)] How many bacteria will be present after 12 hours?
    \item[(b)] After how many hours will the population reach 2,000? (Round to two decimal places)
    \item[(c)] By what percentage does the population increase every hour? Justify your answer.
\end{itemize}


\end{document}
