\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 11}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\subsection*{Problem 1}
If an investor has a choice of investing money at 6\% compounded daily or \( 6 \dfrac{1}{8} \%\) compounded quarterly, which is the better choice?

\subsection*{Problem 2}
Find the present value of the given future payment at the specified interest rate:\\
\[
P = S(1 + r)^{-n}
\]
\begin{enumerate}[label=\alph*)]
    \item \$6000 due in 20 years at 5\% compounded annually.\\
    \( P = 6000(1 + 0.05)^{-20} \)
    \item \$9000 due in \(5.5\) years at 8\% compounded quarterly.
\end{enumerate}

\subsection*{Problem 3}
If \$200 is invested at an annual rate of 5\% compounded continuously, find the compound amount at the end of
\begin{enumerate}[label=\alph*)]
    \item 2 years
    \item 5 years
\end{enumerate}

\subsection*{Problem 4}
A trust fund is being set up by a single payment so that at the end of 18 years there will be \$30,000 in the fund. If interest is compounded continuously at an annual rate of 7\%, how much money should be paid into the fund initially?

\subsection*{Problem 5}
Find the present value of a \$20{,}000 payment due in 12 years at an annual interest rate of 4.5\% compounded monthly.

\subsection*{Problem 6}
How much must be invested now at 6.75\% compounded continuously to accumulate \$10{,}000 in 9 years?

\subsection*{Problem 7}
Compare the following two investment options and decide which yields more:
\begin{itemize}
    \item 6.2\% compounded monthly
    \item 6.3\% compounded quarterly
\end{itemize}

\subsection*{Problem 8}
Find the compound amount if \$850 is invested at 9\% compounded continuously for 6 years.

\section*{Problem Set 2\\Difficulty level: Hard}
\subsection*{Problem 1}
You need \$40{,}000 in 15 years for your child’s education. You plan to make a single deposit into an account that earns 5.5\% interest compounded continuously.

\begin{itemize}
    \item[(a)] How much should you deposit now to meet your goal?
    \item[(b)] If you can only invest \$20{,}000 now, what interest rate would you need (compounded continuously) to reach \$40{,}000 in 15 years?
\end{itemize}

Use:
\[
A = Pe^{rt}
\quad \text{and} \quad r = \frac{1}{t} \ln\left(\frac{A}{P}\right)
\]


\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
\textbf{Investing money at 6\% compounded daily}
\[
r_e = \left(1 + \frac{0.06}{365}\right)^{365} - 1
\]
\[
= 6.18\%
\]

\textbf{Investing money at } \( 6\dfrac{1}{8}\%\) \textbf{ compounded quarterly}
\[
r_e = \left(1 + \frac{0.06125}{4} \right)^4 - 1
\]
\[
= 6.27\%
\]

Since the second choice gives the higher effective rate, it is the better choice.
\subsection*{Problem 2}

\begin{itemize}
    \item[(a)] \$6000 due in 20 years at 5\% compounded annually
    \[
    P = 6000(1 + 0.05)^{-20} \approx \boxed{2261.34}
    \]

    \item[(b)] \$9000 due in \(5\dfrac{1}{2}\) years at 8\% compounded quarterly
    \[
    P = 9000 \left(1 + \frac{0.08}{4} \right)^{-22} \approx  \boxed{5821.55}
    \]
\end{itemize}
\subsection*{Problem 3}

\begin{itemize}
    \item[(a)] 2 years
    \[
    S = Pe^{rt}
    \]
    \[
    S = 200e^{0.05 \cdot 2}
    \]
    \[
    S \approx \boxed{221.03}
    \]

    \item[(b)] 5 years
    \[
    S = 200e^{0.05 \cdot 5}
    \]
    \[
    S \approx \boxed{256.81}
    \]
\end{itemize}
\subsection*{Problem 4}

\[
P = Se^{-rt}
\]
\[
P = 30{,}000e^{-18 \cdot 0.07}
\]
\[
P \approx \boxed{8509.62}
\]


\end{document}
