\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Pre-Statistics Test Review 1}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\subsection*{Problem 1}
Evaluate the expression:  
\[
13 - (7 - 11) + 2
\]

\subsection*{Problem 2}
Evaluate the expression:  
\[
2 - 1 + 7 - (-8) + 10 - 9
\]

\subsection*{Problem 3}
Add or divide. Write your answers as simplified fractions or integers:
\begin{enumerate}[label=\alph*)]
  \item \(\dfrac{2}{3} + \dfrac{2}{6}\)
  \item \(\dfrac{2}{3} \div \dfrac{5}{6}\)
\end{enumerate}

\subsection*{Problem 4}
Vanessa is baking chocolate chip cookies and oatmeal cookies.  
She needs \(\dfrac{1}{3}\) cup of sugar for the chocolate chip cookies and \(\dfrac{3}{4}\) cup of sugar for the oatmeal cookies.  
How much sugar (in cups) does she need altogether?

\subsection*{Problem 5}
Find each of the following expressions:
\begin{enumerate}[label=\alph*)]
  \item \((18 + 7)(6 + 2)\)
  \item \((18 + 7) \cdot 6 + 2\)
  \item \(18 + 7 \cdot 6 + 2\)
  \item \(18 + 7 \cdot (6 + 2)\)
\end{enumerate}

\subsection*{Problem 6}
Find the difference:  
\[
-77 - 32 - 3
\]

\subsection*{Problem 7}
Simplify the expression by removing symbols of grouping and combining like terms:  
\[
5(2r - 4s) - 5(5r - 2s)
\]

\subsection*{Problem 8}
Simplify the complex fraction. Write your answer as a simplified fraction or integer:  
\[
\dfrac{8}{11} \div \dfrac{12}{5}
\]

\subsection*{Problem 9}
A space shuttle orbiting Earth travels a distance of about 66 miles in 6 seconds.  
What is the average speed of the space shuttle in miles per second?

\subsection*{Problem 10}
Subtract and simplify:  
\[
(8n^3 - 7n + 2) - (3n^3 + n^2 - 9) + 8n
\]

\subsection*{Problem 11}
Find the product. Simplify your answer completely:  
\[
(3x - 5)(4x + 2)
\]

\subsection*{Problem 12}
Simplify:  
\[
(2x^8 y)^3
\]

\subsection*{Problem 13}
Simplify. Assume no division by zero:  
\[
\dfrac{y^3 y^2}{y^{16} y^3}
\]

\subsection*{Problem 14}
Simplify:  
\[
4x - 3x^2 + 6 - 6x + 2.8 + 4x + 9x^2
\]

\subsection*{Problem 15}
Simplify the expression:  
\[
(-3y)(-8y)(2y)
\]

\subsection*{Problem 16}
Evaluate the expression:  
\[
9 - 8 \div 4 + 2(3)
\]

\subsection*{Problem 17}
Simplify the given expression:  
\[
2(9) - 72 \div 3^2
\]

\subsection*{Problem 18}
Evaluate \(b^2 - 4ac\) for \(a = 3,\ b = 4,\ c = -2\)

\subsection*{Problem 19}
Evaluate \(b^2 - 4ac + 2ac\) for \(a = -2,\ b = 1,\ c = -3\)

\subsection*{Problem 20}
At the beginning of a month, your account balance was \$54.  
During the month, you deposited \$505 and wrote a check for \$470.  
What was your balance at the end of the month?

\end{document}
