\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 12}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\section*{Problem 1}
Find the present value of an annuity of \$100 per month for \(3 \dfrac{1}{2}\) years at an interest rate of 6\% compounded monthly:
\[
A = R \cdot \dfrac{1 - (1 + r)^{-n}}{r}
\]

\section*{Problem 2}
If \$10,000 is used to purchase an annuity consisting of equal payments at the end of each year for the next four years and the interest rate is 6\% compounded annually, find the amount of each payment.

\section*{Problem 3}
If \$20,000 is used to purchase an annuity consisting of equal payments at the end of each year for the next eight years and the interest rate is 6\% compounded annually, find the amount of each payment.
\[
R = \dfrac{A}{\dfrac{1 - (1 + r)^{-n}}{r}}
\]

\section*{Problem 4}
Find the present value of an annuity of \$200 per month for \(3.5\) years at an interest rate of 6\% compounded monthly.
\[
A = R \cdot \dfrac{1 - (1 + r)^{-n}}{r}
\]

\section*{Problem 5}
Over a five-year period, an original principal of \$4000 accumulated to \$4950 in an account in which interest was compounded quarterly. Determine the effective rate of interest, rounded to two decimal places.
\[
A = P \left(1 + \dfrac{r}{n} \right)^{nt} \quad \text{and} \quad r_e = \left(1 + \dfrac{r}{n} \right)^n - 1
\]

\subsection*{Problem 6}
Find the future value of an annuity of \$150 deposited monthly for 5 years at an interest rate of 4.8\% compounded monthly.

\[
A = R \cdot \dfrac{(1 + r)^n - 1}{r}
\]

\subsection*{Problem 7}
If \$8000 is used to purchase an annuity that pays equal yearly amounts for the next 6 years at 5\% interest compounded annually, find the amount of each payment.

\subsection*{Problem 8}
Find the present value of an annuity of \$250 per month for 4 years at 7.2\% compounded monthly.

\section*{Problem Set 2\\Difficulty level: Hard}
\section*{Problem 1}
You are planning to retire in 30 years and want to have \$1,000,000 saved by then. You decide to deposit a fixed amount at the end of every month into an account earning 6.5\% interest compounded monthly.

\begin{itemize}
    \item[(a)] How much should you deposit each month to reach your goal?
    \item[(b)] If you can only afford \$900 per month, how many years will it take to reach \$1,000,000?
\end{itemize}

Use:
\[
A = R \cdot \dfrac{(1 + r)^n - 1}{r} \quad \text{and solve for \( n \) using logs if needed}
\]



\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
\(R = 100,\quad r = 0.06/12 = 0.005,\quad n = 3.5 \cdot 12 = 42\)

So
\[
A = 100 \cdot \frac{1 - (1 + 0.005)^{-42}}{0.005}
\]
\[
A = \boxed{3779.83}
\]
\subsection*{Problem 2}
We are looking to find \( R \)

\[
R = \frac{A}{\frac{1 - (1 + r)^{-n}}{r}}
\]

Given: \( A = 10{,}000 \), \( r = 0.06 \), \( n = 4 \)

\[
R \approx \boxed{2885.91}
\]
\subsection*{Problem 3}
Given: \( A = 20{,}000 \), \( r = 0.06 \), \( n = 8 \)

\[
R = \frac{20{,}000}{\frac{1 - (1 + 0.06)^{-8}}{0.06}}
\]

\[
R \approx \boxed{3220.72}
\]

\subsection*{Problem 4}
Given: \( R = 200 \), \( r = \frac{0.06}{12} = 0.005 \), \( n = 3.5 \cdot 12 = 42 \)

\[
A = 200 \cdot \frac{1 - (1 + 0.005)^{-42}}{0.005}
\]

\[
A \approx  \boxed{7559.66}
\]

\subsection*{Problem 5}
Find the nominal rate first:

\[
4950 = 4000 \left(1 + \frac{r}{4}\right)^{4 \cdot 5} = 4000 \left(1 + \frac{r}{4}\right)^{20}
\]

\[
1 + \frac{r}{4} = 20\sqrt{\frac{4950}{4000}} \Rightarrow \frac{r}{4} = 0.0107 \Rightarrow r = 4 \cdot 0.0107 \approx \boxed{4.28\%}
\]

Now find the effective rate:

\[
r_e = \left(1 + \frac{r}{n} \right)^n - 1 \quad \text{so} \quad r_e = (1.0107)^4 - 1 \approx \boxed{4.35\%}
\]

\end{document}
