\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Exam Review 2}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}

\subsection*{Problem 1: Radioactive Decay}
A radioactive element is such that \( N \) grams remain after \( t \) hours, where
\[
N = 12e^{-0.031t}.
\]
\begin{enumerate}[label=(\alph*)]
    \item How many grams are initially present?
    \item To the nearest tenth of a gram, how many grams remain after 10 hours?
    \item How many grams remain after 44 hours?
\end{enumerate}

\subsection*{Problem 2: Supply Equation}
A manufacturer’s supply equation is 
\[
p = \log\left(10 + \dfrac{q}{2}\right),
\]
where \( q \) is the number of units supplied at price \( p \) per unit.\\
At what price will the manufacturer supply 1980 units?

\subsection*{Problem 3: Logarithmic Expressions}
Rewrite the expression as a single logarithm.
\begin{enumerate}[label=(\alph*)]
    \item \( 5\left(2\log x + 3\log y - 2\log z\right) \)
    \item \( \ln(x - 4) + \ln(3) - 4\ln x \)
\end{enumerate}

\subsection*{Problem 4: Exponential Equations}
Solve the following exponential equations, that is, find \( x \).
\begin{enumerate}[label=(\alph*)]
    \item \( 81^{4x} = 9 \)
    \item \( 5(3^x - 7) = 10 \)
\end{enumerate}

\subsection*{Problem 5: Logarithmic Expressions}
Find the exact value of the logarithmic expression.
\begin{enumerate}[label=(\alph*)]
    \item \( \log_{10} 100 \)
    \item \( \log_{7}\left( \dfrac{1}{343} \right) \)
\end{enumerate}

\subsection*{Problem 6: Plant Population Model}
In a study of rooted plants in a certain geographic region, it was determined that on plots of size \( A \) (in square meters), the average number of species that occurred was \( S \). When \( \log S \) was graphed as a function of \( \log A \), the result was a straight line given by
\[
\log S = \log 12.4 + \log A
\]
Solve for \( S \).

\subsection*{Problem 7: Compound Interest}
Suppose \$500 are invested at a nominal rate of 5.5\% compounded semiannually.\\
Calculate the amount after three years using the formula:
\[
S = P(1 + r)^n
\]

\subsection*{Problem 8: Effective Interest Rate}
An investor has a choice of investing a sum of money at 8\% compounded annually or at 7.8\% compounded semiannually.\\
Which is the better of the two rates? Compare the effective rates using the formula:
\[
r_e = \left(1 + \dfrac{r}{n} \right)^n - 1
\]

\subsection*{Problem 9: Present Value with Continuous Compounding}
A trust fund is being set up by a single payment so that at the end of 30 years there will be \$50{,}000 in the fund.\\
If interest is compounded continuously at an annual rate of 6\%, how much money should be paid into the fund initially?

Use the formula:
\[
P = Se^{-rt}
\]

\subsection*{Problem 10: Present Value of an Annuity}
Find the present value of an ordinary annuity if \$2000 are paid per quarter for \( 4.5 \) years at a rate of 8\% compounded quarterly.

Use the formula:
\[
A = R \cdot \dfrac{1 - (1 + r)^{-n}}{r}
\]

\subsection*{Problem 11: Loan Amortization}
A person is amortizing a 36-month car loan of \$7500 with an interest rate of 4\% compounded monthly. Find the principal remaining after 9 months by computing:
\[
R \cdot \dfrac{1 - (1 + r)^{(-n + k - 1)}}{r}
\]


\newpage
\section*{Solutions to the Set 1}

\subsection*{Problem 1}
\begin{enumerate}[label=(\alph*)]
    \item 
    \[
    N = 12e^{-0.031t} = 12e^{-0.031(0)} = \boxed{12 \text{ grams}}
    \]

    \item 
    \[
    t = 10,\quad N = 12e^{-0.031(10)} = 12e^{-0.31} \approx \boxed{8.8 \text{ grams}}
    \]

    \item 
    \[
    t = 44,\quad N = 12e^{-0.031(44)} = 12e^{-1.364} \approx \boxed{3.07 \text{ grams}}
    \]
\end{enumerate}

\subsection*{Problem 2}
\[
p = \log\left(10 + \dfrac{1980}{2}\right) = \boxed{3}
\]

\subsection*{Problem 3}
\begin{enumerate}[label=(\alph*)]
    \item 
    \[
    5\left(2\log x + 3\log y - 2\log z\right) = 10\log x + 15\log y - 10\log z
    \]
    \[
    = \log x^{10} + \log y^{15} + \log z^{-10}
    = \log\left(\dfrac{x^{10} y^{15}}{z^{10}}\right)
    \]

    \item 
    \[
    \ln(x - 4) + \ln(3) - 4\ln x 
    = \ln\left[(x - 4)(3)\right] - \ln(x^4)
    \]
    \[
    = \ln\left(\dfrac{3x - 12}{x^4}\right)
    \]
\end{enumerate}

\subsection*{Problem 4}
\begin{enumerate}[label=(\alph*)]
    \item 
    \[
    81^{4x} =9 \implies x= \boxed{\dfrac{1}{8}}
    \]

    \item 
    \[
    5(3^x - 7) = 10 \implies x = \boxed{2}
    \]
\end{enumerate}

\subsection*{Problem 5}
\begin{enumerate}[label=(\alph*)]
    \item 
    \[
    \log_{10}(100) = \boxed{2}
    \]

    \item 
    \[
    \log_{7}\left(\dfrac{1}{343}\right) = \log_{7}(7^{-3}) = \boxed{-3}
    \]
\end{enumerate}

\subsection*{Problem 6}
\[
\ln S = \ln 12.6 + \ln A \Rightarrow \ln S = \ln(12.6A) \Rightarrow S = 12.6A
\]
\[
\text{If } A = 1, \text{ then } S = \boxed{12.6}
\]

\subsection*{Problem 7}
\[
S = 500\left(1 + \dfrac{0.055}{2}\right)^6 \approx \boxed{588.38}
\]

\subsection*{Problem 8}
\textbf{Choice 1: 8\% compounded annually}
\[
r_e = \left(1 + \dfrac{0.08}{1}\right)^1 - 1 = 0.08 = \boxed{8\%}
\]

\textbf{Choice 2: 7.8\% compounded quarterly}
\[
r_e = \left(1 + \dfrac{0.078}{4}\right)^4 - 1 \approx 0.0803 = \boxed{8.03\%}
\]

Since the second choice gives the higher effective rate, \textbf{it is the better choice}.

\subsection*{Problem 9}
\[
P = Se^{-rt} = 50000 \cdot e^{-0.06 \cdot 30}  \approx \boxed{8264.94}
\]

\subsection*{Problem 10}
Data: \( R = 2000 \), \( r = \dfrac{0.08}{4} = 0.02 \), \( n = 4 \cdot 4.5 = 18 \)

\[
A = 2000 \cdot \dfrac{1 - (1 + 0.02)^{-18}}{0.02} \approx \boxed{29{,}984.06}
\]

\subsection*{Problem 11}
Data: \( A = 7500 \), \( n = 36 \), \( r = \dfrac{0.04}{12} \)

\[
R = \dfrac{7500}{\dfrac{1 - (1 + 0.04/12)^{-36}}{0.04/12}} \approx \boxed{221.43}
\]

\textbf{The principal remaining after 9 months by computing}
\[
P = 221.43 \cdot \dfrac{1 - (1 + 0.04/12)^{-27}}{0.04/12} \approx \boxed{5706.57}
\]

\end{document}
