\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Pre-Statistics Worksheet 7}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Write the expression or phrase}

\subsection*{Problem 1}
Write an expression for “5 less than \(x\).”

\subsection*{Problem 2}
Write an expression for “9 increased by \(x\).”

\subsection*{Problem 3}
Write an algebraic expression for the verbal expression “\(q\) times \(b\).”

\subsection*{Problem 4}
Write an expression for “the quotient of 12 and \(x\).”

\subsection*{Problem 5}
Write a word phrase for the algebraic expression \(4n - 7\).

\subsection*{Problem 6}
Translate the expression \(4(x - 7) - 4\) into a verbal phrase.

\subsection*{Problem 7}
Write the expression \(\dfrac{x + y + z}{4}\) using English words.

\section*{Translate to an equation, and solve for (8-14)}

\subsection*{Problem 8}
“Seven more than \(x\) is equal to 54.”

\subsection*{Problem 9}
“Ten less than \(m\) is \(-13\).”

\subsection*{Problem 10}
The sum of \(y\) and \(-20\) is 60.

\subsection*{Problem 11}
The difference of \(8x\) and \(5x\) is 115.

\subsection*{Problem 12}
Mollie paid \$43.75 for 6 movie tickets. What was the price (in dollars) of each ticket?

\subsection*{Problem 13}
Connie’s kindergarten class has 28 children. She wants them to get into 4 equal groups. How many children will she put in each group?

\subsection*{Problem 14}
The quotient of \(k\) and 22 is \(-88\).

\subsection*{Problem 15}
Translate and solve: “Six times a number \(n\) decreased by 4 is 38.”

\subsection*{Problem 16}
Write an algebraic expression for: “The total of twice a number and 11.”

\subsection*{Problem 17}
Translate the phrase into an equation and solve: “The quotient of a number \(x\) and 3 is equal to 9.”

\subsection*{Problem 18}
Write an algebraic expression for:  
“Triple a number decreased by 8.”

\subsection*{Problem 19}
Translate the sentence into an equation and solve:  
“The sum of twice a number and 5 is 19.”

\subsection*{Problem 20}
Jamal earns \$12.50 per hour. If he earned \$137.50 one week, how many hours did he work?

\subsection*{Problem 21}
Solve for \(x\):  
\[
4x + 7 = 31
\]

\subsection*{Problem 22}
Solve for \(x\):  
\[
3(x - 2) = 27
\]

\subsection*{Problem 23}
Solve for \(x\):  
\[
\dfrac{2x - 5}{3} = 11
\]

\end{document}
