\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 5}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\section*{Problem 1}
Solve the systems algebraically:

\begin{enumerate}[label=(\alph*)]
    \item 
    \[
    \begin{cases}
    x + 4y = 3 \\
    3x - 2y = -5
    \end{cases}
    \]
    
    \item 
    \[
    \begin{cases}
    2x + 3y = 1 \\
    x + 2y = 0
    \end{cases}
    \]
    
    \item 
    \[
    \begin{cases}
    2p + 3q = 5 \\
    10p + 15q = 0
    \end{cases}
    \]
    
    \item 
    \[
    \begin{cases}
    p^2 = 5 - q \\
    p = q + 1
    \end{cases}
    \]
    
    \item 
    \[
    \begin{cases}
    4x + 5y = 335 \\
    9x + 14y = 850
    \end{cases}
    \]
\end{enumerate}

\section*{Problem 2}
A computer consultant has \$200{,}000 invested for retirement, part at 9\% and part at 8\%. If the total yearly income from the investments is \$17{,}200, how much is invested at each rate?

\section*{Problem 3}
A company pays its salespeople on a basis of a certain percentage of the first \$100{,}000 in sales, plus a certain percentage of any amount over \$100{,}000 in sales. If one salesperson earned \$8{,}500 on sales of \$175{,}000 and another salesperson earned \$14{,}800 on sales of \$280{,}000, find the two percentages.

\section*{Problem 4}
A total of \$12,000 is invested in two accounts. One account earns 6\% annual interest, and the other earns 9\%. After one year, the total interest earned from both accounts is \$870. How much was invested in each account?

\section*{Problem 5}
Two numbers have a sum of 45. Three times the first number plus twice the second number is 106. Find the two numbers.

\section*{Problem 6}
A rental car company charges a flat fee plus a charge per mile driven. One customer rented a car and drove 120 miles, paying \$78. Another customer drove 200 miles and paid \$114. Find the flat fee and the cost per mile.

\section*{Problem Set 2\\Difficulty level: Hard}
\section*{Problem 1}
Consider the system of equations:
\[
\begin{cases}
kx + 4y = 12 \\
3x - 2y = -6
\end{cases}
\]

\begin{enumerate}[label=(\roman*)]
    \item Find the value(s) of \( k \) for which the system has:
    \begin{itemize}
        \item exactly one solution
        \item no solution
        \item infinitely many solutions
    \end{itemize}
    \item For \( k = 6 \), solve the system algebraically.
\end{enumerate}

\end{document}
