\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 4}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\section*{Problem 1}
Find the vertex and intercepts for each function:
\begin{enumerate}[label=(\alph*)]
    \item \( f(x) = x^2 - 6x + 5 \)
    \item \( f(s) = s^2 - 8s + 14 \)
\end{enumerate}

\section*{Problem 2}
The daily profit for the garden department of a store from the sale of trees is given by:
\[
P(q) = -q^2 + 18q + 144
\]
where \( q \) is the number of trees sold. Find the function’s vertex and intercepts and graph the function.

\section*{Problem 3}
State whether \( f(x) \) has a maximum value or a minimum value, and find that value:
\begin{enumerate}[label=(\alph*)]
    \item \( f(x) = 49x^2 - 10x + 17 \)
    \item \( f(x) = -7x^2 - 2x + 6 \)
\end{enumerate}

\section*{Problem 4}
The demand function for a manufacturer’s product is 
\[
p = f(q) = 100 - 10q,
\]
where \( p \) is the price (in dollars) per unit when \( q \) units are demanded (per day). Find the level of production that maximizes the manufacturer’s total revenue and determine this revenue.

\section*{Problem 5}
Find the vertex and intercepts for each function:
\begin{enumerate}[label=(\alph*)]
    \item \( f(x) = -2x^2 + 4x + 6 \)
    \item \( f(y) = 3y^2 + 12y + 9 \)
\end{enumerate}

\section*{Problem 6}
A company’s weekly profit (in dollars) from selling boxes is given by:
\[
P(n) = -5n^2 + 40n - 60,
\]
where \( n \) is the number of boxes sold. Find the vertex and intercepts of the profit function.

\section*{Problem 7}
State whether \( f(x) \) has a maximum or minimum value, and find that value:
\begin{enumerate}[label=(\alph*)]
    \item \( f(x) = -4x^2 + 16x + 1 \)
    \item \( f(x) = 2x^2 + 8x + 3 \)
\end{enumerate}

\section*{Problem 8}
The revenue function for a local theater is:
\[
R(t) = t(20 - t),
\]
where \( t \) is the price (in dollars) of a ticket and \( R(t) \) is the total revenue from ticket sales. Find the ticket price that maximizes revenue and determine the maximum revenue.

\section*{Problem Set 2\\Difficulty level: Hard}
\section*{Problem 1}
A business models its total daily profit from selling a product as:
\[
P(x) = -2x^2 + 40x - 120,
\]
where \( x \) is the number of items sold, and \( P(x) \) is the profit in dollars.

However, due to warehouse limitations, the company cannot produce more than 20 units per day.

\begin{enumerate}[label=(\alph*)]
    \item Find the number of items that maximizes the profit.
    \item Determine the maximum profit.
    \item Find the \( x \)- and \( y \)-intercepts of the profit function.
    \item Determine the range of production levels (values of \( x \)) that result in a profit of at least \$200.
\end{enumerate}

\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
\subsection*{Problem 2}
\subsection*{Problem 3}
\subsection*{Problem 4}
\subsection*{Problem 5}
\subsection*{Problem 6}
\subsection*{Problem 7}
\subsection*{Problem 8}
\section*{Solutions to the Set 2}
\subsection*{Problem 1}

\end{document}
