\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 10}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\subsection*{Problem 1}
How long will it take for \$600 to amount to \$900 at an annual rate of 6\% compounded quarterly?\\
Use the formula:
\[
A = P\left(1 + \frac{r}{n} \right)^{nt}
\]

\subsection*{Problem 2}
Find the amount or future value when a principal of \$18{,}000 is invested at 9.5\% compounded daily for 3 years?\\
Use the formula:
\[
A = P\left(1 + \frac{r}{n} \right)^{nt}
\]

\subsection*{Problem 3}
What effective rate is equivalent to a nominal rate of 7\% compounded:
\begin{itemize}
    \item[(a)] semiannually
    \item[(b)] quarterly
\end{itemize}
Use the formula:
\[
r_e = \left(1 + \frac{r}{n} \right)^n - 1
\]

\subsection*{Problem 4}
Over a five-year period, an original principal of \$2000 accumulated to \$2950 in an account in which interest was compounded quarterly. Determine the effective rate of interest, rounded to two decimal places.\\
Recall,
\[
A = P\left(1 + \frac{r}{n} \right)^{nt}
\qquad \text{and} \qquad
r_e = \left(1 + \frac{r}{n} \right)^n - 1
\]

\subsection*{Problem 5}
How long will it take for \$1500 to double in value if it is invested at 8\% compounded monthly?\\
Use:
\[
A = P\left(1 + \frac{r}{n} \right)^{nt}
\]

\subsection*{Problem 6}
Find the future value of an investment of \$10{,}000 at 5.25\% compounded monthly for 4.5 years.

\subsection*{Problem 7}
Find the effective rate corresponding to a nominal rate of 6.8\% compounded monthly.

\subsection*{Problem 8}
An investment grows from \$2500 to \$3800 in 6 years with interest compounded annually. Find the annual interest rate to the nearest hundredth of a percent.

\section*{Problem Set 2\\Difficulty level: Hard}
\subsection*{Problem 1}
You want to have \$50{,}000 in your account in 8 years. You found a savings account that pays 4.8\% annual interest compounded monthly.

\begin{itemize}
    \item[(a)] How much should you invest now to reach your goal?
    \item[(b)] If you can only invest \$35{,}000 now, how many additional months would it take to reach \$50{,}000 at the same interest rate?
\end{itemize}


\end{document}
