\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 8}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}

\section*{Problem 1}
Find \( x \):
\begin{enumerate}[label=(\alph*)]
    \item \( \log_3 x = 4 \)
    \item \( \log_x \dfrac{1}{6} = -1 \)
    \item \( \log_x 25 = 2 \)
    \item \( \log_8 64 = x - 1 \)
\end{enumerate}

\section*{Problem 2}
The cost for a firm producing \( q \) units of a product is given by the cost equation:
\[
c = (5q \ln q) + 15
\]
Evaluate the cost when \( q = 12 \). (Round your answer to two decimal places.)

\section*{Problem 3}
A manufacturer’s supply equation is 
\[
p = \log\left(10 + \frac{q}{2} \right)
\]
Where \( q \) is the number of units supplied at price \( p \) per unit. At what price will the manufacturer supply 1980 units?

\section*{Problem 4}
If \$15,650 is invested at 7\% compounded monthly, then how long will it take for the investment to grow to \$63,450?\\
Hint: 
\[
A = P \left(1 + \frac{r}{n} \right)^{nt}
\]

\section*{Problem 5}
Solve for \( x \):
\begin{enumerate}[label=(\alph*)]
    \item \( \ln(x - 3) - \ln(10) = \ln(15) \)
    \item \( \log(x - 3) + \log(x + 3) = 2 \)
\end{enumerate}

\section*{Problem 6}
The number of grams of a certain radioactive substance present at time \( t \) is given by the formula:
\[
A(t) = 400 \cdot e^{-0.0002t}
\]
How many grams are present at time \( t = 0 \)?\\
How many grams are present at time \( t = 600 \)? Round to the nearest gram.

\begin{itemize}
    \item[a.] 200 grams, 121 grams
    \item[b.] 400 grams, 242 grams
    \item[c.] 600 grams, 363 grams
    \item[d.] 400 grams, 355 grams
\end{itemize}

\section*{Problem 7}
A certificate of deposit is purchased for \$6500 and is held for three years. If the certificate earns 2\% compounded quarterly, what is it worth at the end of three years?

\section*{Problem 8}
Solve the equation:
\[
\log(2x + 1) + \log(5) = 2
\]
(Hint: Use logarithmic properties and solve for \( x \). Round your final answer to two decimal places if needed.)

\section*{Problem Set 2\\Difficulty level: Hard}
\section*{Problem 1}
You invest \$10{,}000 in an account earning 6.5\% interest compounded monthly. You want it to grow to \$25{,}000.

\begin{itemize}
    \item[(a)] How many years will it take to reach your goal?
    \item[(b)] After how many full years will the investment be worth **at least double** its original value?
\end{itemize}

Use the compound interest formula:
\[
A = P \left(1 + \frac{r}{n} \right)^{nt}
\]



\end{document}
