\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{College Algebra Worksheet 6.6}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}

\subsection*{Problem 1}
Which is the solution to \( 5^{5x} = 5^{x+2} \)?  
\begin{enumerate}[label=(\alph*)]
    \item \( \dfrac{1}{6} \)
    \item \( \dfrac{1}{4} \)
    \item \( \dfrac{1}{2} \)
    \item \( 2 \)
    \item \( 4 \)
\end{enumerate}

\subsection*{Problem 2}
Determine the value of \( x \) which satisfies the following equation.
\[ 16^{-2x+2} = 64^{-2x+2} \]

\subsection*{Problem 3}
Solve \( 5^{x-3} = 7^x \).

\subsection*{Problem 4}
Which is the solution to \( 7e^{9x} = 20 \), rounded to the nearest tenth?

\begin{enumerate}[label=(\alph*)]
    \item \( x = -0.6 \)
    \item \( x = 0.3 \)
    \item \( x = 0.1 \)
    \item \( x = -0.2 \)
    \item \( x = -0.3 \)
\end{enumerate}

\subsection*{Problem 5}
Find the value of \( x \) which satisfies the following equation.
\[\log_3(7x-26)=2\]

\subsection*{Problem 6}
Solve the following equation for \(x\).
\[ \log_3(x + 8) + \log_3(x) = 2 \]  

\subsection*{Problem 7}
Which value makes the equation \( \log[3(x + 1)] = \log[3(2x)] \) true?

\begin{enumerate}[label=(\alph*)]
    \item \( x = 5 \)
    \item \( x = 4 \)
    \item \( x = 3 \)
    \item \( x = 2 \)
    \item \( x = 1 \)
\end{enumerate}

\subsection*{Problem 8}
A virus takes 8 days to double its original population \((A=2A_0)\). How long will it take to quadruple its population?  
Round to the nearest tenth.


\subsection*{Problem 9}
Sal invests \$16,000 at age 35. He hopes the investment will be worth \$320,000 when he turns 40.  
If the interest compounds continuously, approximately what rate of growth will he need to achieve his goal?  
Round to the nearest tenth of a percent.


\subsection*{Problem 10}
A bacteria population declined from 470,000 to 500 in 24 hours.  
At this rate of decay, how many bacteria will there be in 18 hours?  
Round to the nearest whole number.

\section*{Problem Set 2\\Difficulty level: Hard}
\subsection*{Problem 1}
For the following exercises, use logarithms to solve.
\begin{enumerate}[label=(\alph*)]
    \item \( e^{2x} - e^x - 132 = 0 \)
    \item \( 7e^{8x+8} - 5 = -95 \)
    \item \( 10e^{8x+3} + 2 = 8 \)
    \item \(-8 \cdot 10^{p+7}-7=-24\)
\end{enumerate}


\newpage
\section*{Solutions to the Set 1}

\subsection*{Problem 1}
(a) \( \dfrac{1}{2} \)

\subsection*{Problem 2}
1

\subsection*{Problem 3}
\(x=\dfrac{3\ln(5)}{\ln(5)-\ln(7)}\)

\subsection*{Problem 4}
\begin{enumerate}
    \item[(c)] \(x=0.1\)
\end{enumerate} 

\subsection*{Problem 5}
\( x = 5 \)

\subsection*{Problem 6}
\( x = 1 \)

\subsection*{Problem 7}
(e) \( x = 1 \)

\subsection*{Problem 8}
16 days

\subsection*{Problem 9}
59.9\%

\subsection*{Problem 10}
2769 bacteria

\section*{Solutions to the Set 2}
\subsection*{Problem 1}
\begin{enumerate}[label=(\alph*)]
    \item $e^{2x} - e^x - 132 = 0$ \\
          Let $y = e^x$: \\
          $y^2 - y - 132 = 0$ \\
          $y = \dfrac{1 \pm \sqrt{1 + 528}}{2} = \dfrac{1 \pm 23}{2}$ \\
          $y = 12$ \quad (since $y = e^x > 0$) \\
          $e^x = 12$ \\
          $x = \ln(12)$

    \item $7e^{8x+8} - 5 = -95$ \\
          $7e^{8x+8} = -90$ \\
          There is no real solution, since $e^{8x+8} > 0$

    \item $10e^{8x+3} + 2 = 8$ \\
          $10e^{8x+3} = 6$ \\
          $e^{8x+3} = 0.6$ \\
          $8x + 3 = \ln(0.6)$ \\
          $x = \dfrac{\ln(0.6) - 3}{8}$

    \item $-8 \cdot 10^{p+7} - 7 = -24$ \\
          $-8 \cdot 10^{p+7} = -17$ \\
          $10^{p+7} = \dfrac{17}{8}$ \\
          $p + 7 = \log_{10}\left(\dfrac{17}{8}\right)$ \\
          $p = \log_{10}(2.125) - 7$
\end{enumerate}

\end{document}
