\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Math for Business \& Social Science\\ Worksheet 16}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\subsection*{Problem 1}
Solve the inequalities:
\begin{enumerate}[label=\alph*)]
    \item \( 3x + 4y > 2 \)
    \item \( 3x - 5y \leq 11 \)
\end{enumerate}

\subsection*{Problem 2}
Solve the inequalities:
\begin{enumerate}[label=\alph*)]
    \item 
    \[
    \left\{
    \begin{aligned}
        3x - 2y &< 6 \\
        x - 3y &> 9
    \end{aligned}
    \right.
    \]
    \item 
    \[
    \left\{
    \begin{aligned}
        x - y &> 4 \\
        x &< 2 \\
        y &> -5
    \end{aligned}
    \right.
    \]
\end{enumerate}

\subsection*{Problem 3}
A store sells two types of cameras. In order to cover overhead, it must sell at least 50 cameras per week, and in order to satisfy distribution requirements, it must sell at least twice as many of type I as type II.\\

Let \(x\) be the number of type I cameras and \(y\) the number of type II cameras sold in a week.\\

Write a system of inequalities to describe the situation and find the region defined by the system.

\subsection*{Problem 4}
Solve the inequality and graph the solution region:
\[
2x + y \leq 6
\]

\subsection*{Problem 5}
Solve the system of inequalities and describe the feasible region:
\[
\left\{
\begin{aligned}
x + 2y &\geq 8 \\
3x - y &< 12
\end{aligned}
\right.
\]

\subsection*{Problem 6}
A company produces tables and chairs. Each table takes 4 hours of labor and each chair takes 2 hours. The company has a maximum of 100 labor hours available per week. To meet customer demand, it must produce at least 5 tables and at least 10 chairs per week.

Let \( x \) be the number of tables and \( y \) the number of chairs. Write a system of inequalities to represent this situation.

\section*{Problem Set 2\\Difficulty level: Hard}
\subsection*{Problem 1}
A manufacturer produces two products, A and B. Each unit of A requires 3 hours of machining and 1 hour of assembly. Each unit of B requires 2 hours of machining and 2 hours of assembly. The manufacturer has 60 machining hours and 40 assembly hours available per week. In addition, at least 5 units of product A and at least 10 units of product B must be produced to meet minimum contractual obligations.

Let \( x \) be the number of units of A and \( y \) the number of units of B.

\begin{enumerate}[label=\alph*)]
    \item Write a system of inequalities representing this situation.
    \item Graph the feasible region.
\end{enumerate}


\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
See the solution for \((a)\) in \href{https://www.desmos.com/calculator/gprmyamv3v}{here}, and for \((b)\) in \href{https://www.desmos.com/calculator/tab5i4blid}{here}.
\subsection*{Problem 2}
See the solution for \((a)\) in \href{https://www.desmos.com/calculator/i4y7nlqmw9}{here}, and for \((b)\) in \href{https://www.desmos.com/calculator/ufjpe021nr}{here}.

\subsection*{Problem 3}
It must sell at least 50 cameras per week:
\[
x + y \geq 50
\]

It must sell at least twice as many of type I as type II:
\[
2x \geq y
\]

Therefore, the two inequalities are:
\[
\left\{
\begin{aligned}
x + y &\geq 50 \\
2x &\geq y
\end{aligned}
\right.
\]
See the graph in \href{https://www.desmos.com/calculator/tttrsi9oqp}{here}.

\end{document}
