\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{College Algebra Worksheet 5.5}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\subsection*{Problem 1}
Find the real zeros of the following polynomial.
\[f(x)=x^4-8x\]

\subsection*{Problem 2}
According to the Factor Theorem, which are the zeros of \(f(x)=2x^3-22x^2+72x-72\) given that \((x-6)\) is a factor of the polynomial?

\subsection*{Problem 3}
Consider the function \(f(x)=x^3+5x^2-44x+60\). If \(f(x)=0\) for \(x=-10\), for what other values of \(x\) is the function equal to \(0\)?

\subsection*{Problem 4}
For what values of \(x\) is \(x^3+x^2-122x+120=0\) a true statement?

\subsection*{Problem 5}
For what values of \(x\) is \(x^3+20x^2+89x+70=0\) a true statement?

\subsection*{Problem 6}
Find the real zeros of the following polynomial.
\[f(x)=x^6-3x^4-28x^2\]

\subsection*{Problem 7}
Find the zeros of the following polynomial.
\[f(x)=x^5+6x^4+9x^3\]

\subsection*{Problem 8}
Find the zeros of the following polynomial.
\[f(x)=x^4+2x^3-3x^2\]

\subsection*{Problem 9}
Which function has an actual rational zero of 7?
\begin{enumerate}
    \item[(a)] \(g(x)=x^3-4x^2-26x+28\)
    \item[(b)] \(g(x)=x^3-4x^2-26x+35\)
    \item[(c)] \(g(x)=x^3-4x^2+26x+35\)
    \item[(d)] \(g(x)=x^3+4x^2-26x+35\)
\end{enumerate}

\subsection*{Problem 10}
Use the Rational Zero Theorem to find a rational zero of the function \(f(x)=3x^3+6x^2-20x+16\).

\subsection*{Problem 11}
What are the actual rational zeros of the function \(f(x)=x^3+3x^2-25x+21\)?


\section*{Problem Set 2\\Difficulty level: Hard}
\subsection*{Problem 1}
For the following exercises, use the Rational Zero Theorem to find the real solution(s) to each equation.
\begin{enumerate}
    \item[(a)] \(x^4-2x^3-7x^2+8x+12=0\)
    \item[(b)] \(4x^3-3x+1=0\)
\end{enumerate}


\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
\(x=0,2\)
\subsection*{Problem 2}
\(x=2,3,6\)
\subsection*{Problem 3}
\(x=2,3\)
\subsection*{Problem 4}
\(x=-12,1,10\)
\subsection*{Problem 5}
\(x=-14,-5,-1\)
\subsection*{Problem 6}
\(x=-\sqrt{7},0,\sqrt{7}\)
\subsection*{Problem 7}
\(x=-3,0\)
\subsection*{Problem 8}
\(x=-3,0,1\)
\subsection*{Problem 9}
\begin{enumerate}
    \item[(b)] \(g(x)=x^3-4x^2-26x+35\) 
\end{enumerate}
\subsection*{Problem 10}
\(x=-4\)
\subsection*{Problem 11}
\(x=-7,1,3\)

\section*{Solutions to the Set 2}
\subsection*{Problem 1}
\begin{enumerate}[label=(\alph*)]
    \item For the equation \(x^4 - 2x^3 - 7x^2 + 8x + 12 = 0\):
    \begin{itemize}
        \item Possible rational roots: \(\pm1, \pm2, \pm3, \pm4, \pm6, \pm12\)
        \item Testing roots:
        \begin{itemize}
            \item \(f(-2) = 16 + 16 - 28 - 16 + 12 = 0\) → Factor \((x+2)\)
            \item \(f(-1) = 1 + 2 - 7 - 8 + 12 = 0\) → Factor \((x+1)\)
            \item After factoring out \((x+2)(x+1)\), we get \((x^2 - 5x + 6)\) with roots \(x=2, x=3\)
        \end{itemize}
        \item Final solutions: \(\boxed{x = -2,\; x = -1,\; x = 2,\; x = 3}\)
    \end{itemize}
    
    \item For the equation \(4x^3 - 3x + 1 = 0\):
    \begin{itemize}
        \item Possible rational roots: \(\pm1, \pm\dfrac{1}{2}, \pm\dfrac{1}{4}\)
        \item Testing roots:
        \begin{itemize}
            \item \(f(-1) = -4 + 3 + 1 = 0\) → Factor \((x+1)\)
            \item After factoring out \((x+1)\), we get \((4x^2 - 4x + 1)\) with double root \(x=\dfrac{1}{2}\)
        \end{itemize}
        \item Final solutions: \(\boxed{x = -1,\; x = \dfrac{1}{2}}\)
    \end{itemize}
\end{enumerate}

\end{document}
