\documentclass[12pt]{article}
\usepackage[a4paper, total={5.5in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage{hyperref}

\title{College Algebra Worksheet 7.1}
\author{PCL Learning Center}
\date{}

\begin{document}
\maketitle

\section*{Problem Set 1\\Difficulty level: Normal}
\subsection*{Problem 1}
Solve the following system of equations.
\[
\left\{\begin{aligned}
-7x + 6y &= -10\\[6pt]
x &= -y - 6
\end{aligned}\right.
\]

\subsection*{Problem 2}
Solve the following system of equations.
\[
\left\{\begin{aligned}
-5x - 4y &= -12\\[6pt]
2x + 3y &= 2
\end{aligned}\right.
\]

\subsection*{Problem 3}
Given the values \(x=-4\) and \(z=1\), solve the following system for \(y\):
\[
\left\{\begin{aligned}
-4x + y - z &= 12\\[6pt]
-5x + y + 4z &= 21\\[6pt]
-4x - y + 4z &= 23
\end{aligned}\right.
\]

\subsection*{Problem 4}
Solve the following system of equations.
\[
\left\{\begin{aligned}
2x - 2y - 6z &= -18\\[6pt]
-4x + 3y + 2z &= -4\\[6pt]
-2x - 3y + 2z &= 2
\end{aligned}\right.
\]

\subsection*{Problem 5}
Can a system of linear equations have exactly two solutions? Explain why or why not.

\subsection*{Problem 6}
Given a system of equations, explain at least two different methods of solving that system.

\section*{Problem Set 2\\Difficulty level: Hard}
\subsection*{Problem 1}
Solve the following nonlinear system of equations:
\[
\left\{\begin{aligned}
x^2 + y^2 &= 25 \\[6pt]
y &= 2x + 1
\end{aligned}\right.
\]

\newpage
\section*{Solutions to the Set 1}
\subsection*{Problem 1}
Solution: \(\boxed{(-2,-4)}\)

\subsection*{Problem 2}
Solution: \(\boxed{(4,-2)}\)

\subsection*{Problem 3}
Solution: \(y=\boxed{-3}\)

\subsection*{Problem 4}
Solution: \(\boxed{(3,0,4)}\)

\subsection*{Problem 5}
No, because linear systems can have exactly one solution, no solutions, or infinitely many solutions only.

\subsection*{Problem 6}
Two methods are substitution (isolating one variable and substituting into another equation) and elimination (adding or subtracting equations to eliminate one variable).

\section*{Solutions to the Set 2}
\subsection*{Problem 1}
There are two solutions,
\[
\left\{
\left( \frac{2}{5}\left(\sqrt{31}-1\right),\ \frac{1}{5}\left(1+4\sqrt{31}\right) \right),\quad
\left( -\frac{2}{5}\left(1+\sqrt{31}\right),\ \frac{1}{5}\left(1-4\sqrt{31}\right) \right)
\right\}
\]
See the graph \href{https://www.desmos.com/calculator/7hgg1unnb1}{here}.


\end{document}
